---
title: "Abundance"
format: html
---

{{< include ../_data.qmd >}}

## Function: `getDomainAbundance()`

### Purpose

Calculates relative species abundance at the domain level. This relative estimate is scaled by the total number of PSUs in the Domain.

### Usage

```{r}
#| echo: true
#| eval: false
getDomainAbundance()
```

### Output

```{r}
#| echo: true
#| warning: FALSE
getDomainAbundance(FKEYS2024, "ocy chry") %>% 
  select(YEAR:n) %>% 
  kableExtra::kable()
```

## Function: `getStratumAbundance()`

### Purpose

Calculates relative species abundance at the stratum level. This relative estimate is scaled by the number of PSUs in a given Stratum.

### Usage

```{r}
#| echo: true
#| eval: false
getStratumAbundance()
```

### Output


```{r}
#| echo: true
#| warning: FALSE
getStratumAbundance(FKEYS2024, "ocy chry") %>% 
  select(YEAR:n) %>% 
  kableExtra::kable()
```

## Function: `getPSUAbundance()`

### Purpose

Calculates relative species abundance at the Primary Sample Unit (PSU) level.  This relative estimate is scaled by the number of Secondary Sampling Units (SSU) available in PSU.  

### Usage

```{r}
#| echo: true
#| eval: false
getPSUAbundance()
```

### Output

```{r}
#| echo: true
#| warning: FALSE
getPSUAbundance(FKEYS2024, "ocy chry") %>%
  head() %>% 
  kableExtra::kable()
```