---
title: ""
format: html
number-sections: true
---

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(rvc)
FKEYS2024 <- readRDS("data/FKEYS2024.rds")
```

## Downloading the Data {#sec-GetRvcData}

The following code will retrieve NCRMP fish survey data for the Florida Keys 2024 and save it as a named object in your R environment

```{r}
#| echo: true
#| eval: false
FKEYS2024 <- getRvcData(years = 2024, regions = "FLA KEYS")
```

the 'regions' parameter takes a specific formatted argument

| **"FLA KEYS"** : Florida Keys (Miami/Dade south to Key West)
| **"DRY TORT"** : Dry Tortugas
| **"SEFCRI"** : Southeast Florida (Miami/Dade north to Martin County)
| **"FGBNMS"** : Flower Garden Banks National Marine Sanctuary
| **"PRICO"** : Puerto Rico
| **"STTSTJ"** : St. Thomas and St. John
| **"STX"** : St. Croix

------------------------------------------------------------------------

You can also download multiple years and/or regions into one object (see @sec-AvaliableData)

```{r}
#| echo: true
#| eval: false

# and range of years 1999:2024
All_Keys <- getRvcData(years = 1999:2024, regions = "FLA KEYS") #All years in the Keys

# or 2 specific years in 2 specific regions
USVI <- getRvcData(years = c(2017, 2023), regions = c("STTSTJ", "STX")) #Only 2017 and 2023 in U.S. Virgin Islands
```

## Structure of the data

When using the **getRVCData()** function, the following structure is returned and all other functions in the R-package expect this structure. The object returned is a list of 3 dataframes

1)  sample_data: numbers at length for each species (with some additional meta data)
2)  stratum_data: number of grid cells for each strata (this provided weighting factors)
3)  taxonomic_data: additional species information

```{r}
glimpse(FKEYS2024)
```

## Available Data {#sec-AvaliableData}

**As of Spring 2025**

{{< include _availableData.qmd >}}
